Are We Reusing Outdated Code from Stack Overflow?

### 2017-01-22 cloneoverflow-latex/cloneoverflow.tex
Added heatmap of licenses
Updated the paper.

\documentclass{sig-alternate-05-2015}
\usepackage[utf8]{inputenc}
\usepackage[italian]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{cleveref}

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump is in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We are interested in code snippets embedded in posts which are pieces of code located between \texttt{<code></code>} tags. We filtered the snippets with two filtering criteria. First, we ignore snippets that are less than 6 lines since they are usually not considered as clones by clone detection research \cite{something}. Second, we are only interested in code snippets from posts that are marked as \textbf{accepted answer}. Posts on Stack Overflow are marked accepted by the questions' posters if the solutions in the posts solve their problems. We choose them because they have high chance to be reused than snippets in questions and other answers. Each snippet is extracted from the dump using regular expressions and saved to a file using its post ID as the file's name. If an accepted answer has more than one code snippet, we append an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we add \texttt{.java} extension to the file's names so that clone detectors can recognise them. We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

@@

\begin{table*}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs. S$_u$ denotes a number of unique Stack Overflow snippets. Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
		\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
			\hline
			Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
			\hline 
			\hline
			\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
			\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 29  & 10 & \textbf{47} & 12 & 14 & 10 & 9158 & 35 & 82 & \textbf{9275} & 100 & 204 & 30 & \textbf{9322} & 112 & 218 & 35 \\
			\hline 
			\hline 
			\multirow{1}{*}{\textit{Simian$_{df}$}} & 79 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
			\hline
			\multirow{1}{*}{\textit{NiCad$_{df}$}} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
			\hline
		\end{tabular} 
	}
\end{table*}

@@

@@

\section{Related Work}
\begin{itemize}
	\item Stack Overflow
	\begin{itemize}
		\item Code example \cite{Nasehi2012}
		\item Search for code in Stack Overflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014}
		\item Stack Overflow to help developers \cite{Ponzanelli2013, Ponzanelli2014}
		\item Improving Stack Oveflow \cite{Diamantopoulos2015, Wang2014, Bosu2013}
		\item Developers' behaviours on Stack Overlow \cite{Wang2013_StackOverflow, Movshovitz-Attias2013}
	\end{itemize}
	\item Code clones 
		\begin{itemize}
			\item Definition: Baxter et al. \cite{Baxter1998}
			\item Comparison of clone detectors: \cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}
			\item NiCad \cite{Roy2008,Cordy}
			\item Simian \cite{simian}
			\item Clone taxonomy \cite{Kapser2003}
			\item Clone evolution \cite{Pate2013,Mondal2011}
			\item Comparing Quality Metrics for Cloned and non cloned Java Methods: A Large Scale Empirical Study \cite{Saini2016}.
		\end{itemize}
	\item Agreement-based Clone Detection
	\begin{itemize}
		\item Bellon's framework \cite{Bellon2007}.
		\item EvaClone \cite{Wang2013}
		\item Hybrid \cite{Funaro2010}
	\end{itemize}
	\item Software licensing
	\begin{itemize}
		\item Code siblings \cite{German2009}, Ninka -- Automatic indification of SW license \cite{German2010}, Evolution of SW licensing \cite{DiPenta2010}
	\end{itemize}

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage[utf8]{inputenc}
\usepackage[italian]{babel}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{cleveref}
\usepackage{subcaption}

@@

\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016. The archived dump has a size of 9 gigabytes. The data dump is in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts. We are interested in code snippets embedded in posts which are located between \texttt{<code></code>} tags. A Stack Overflow thread contains a post of question and several posts of answers. Every answer has voting score from users. An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem. We collect Java code snippets using two criteria. First, we are only interested in code snippets with at least six lines. Snippets which are smaller than six lines are usually spurious clones \cite{Bellon2007}. Second, we are only interested in code snippets in accepted answer. We choose snippets in accept answers because they have proofs that they actually solve the problems. Moreover, they are always displayed just below the questions which makes them attractive to be reused than snippets in other answers. Each snippet is extracted from the dump using regular expressions and saved to a file using its post ID as the file's name. If an accepted answer has more than one code snippet, we append an indexing number, starting from zero, after the post ID (e.g. 45051109\_0, and 45051109\_1.). Lastly, we add \texttt{.java} extension to the file's names so that clone detectors can recognise them. We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.

@@

\begin{table*}
	\centering
	\caption{Classification results of agreed and disagreed clone pairs. S$_u$ denotes a number of unique Stack Overflow snippets. Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
	\label{tab:classification_good_o}
	\small
	\resizebox{2.1\columnwidth}{!}{%
		\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
			\hline
			Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
			\hline 
			\hline
			\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
			\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 29  & 10 & \textbf{47} & 12 & 14 & 10 & 9158 & 35 & 82 & \textbf{9275} & 100 & 204 & 30 & \textbf{9322} & 112 & 218 & 35 \\
			\hline 
			\hline 
			\multirow{1}{*}{\textit{Simian$_{df}$}} & 79 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
			\hline
			\multirow{1}{*}{\textit{NiCad$_{df}$}} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
			\hline
			\hline
			Total & 96 & 0 & 396 & 31 & \textbf{523} & -- & -- & -- & 9502 & 107 & 2520 & \textbf{12099} & -- & -- & -- & \textbf{12622} & -- & -- & -- \\ 
			\hline
		\end{tabular} 
	}
\end{table*}

@@

\begin{figure*}
	\minipage{0.32\textwidth}
	\includegraphics[width=\linewidth]{heatmap_a}
	\caption*{(1) category A}\label{fig:heatmap_a}
	\endminipage\hspace{0.3cm}
	\minipage{0.32\textwidth}
	\includegraphics[width=\linewidth]{heatmap_b}
	\caption*{(2) category B}\label{fig:heatmap_b}
	\endminipage\hfill
	\minipage{0.32\textwidth}%
	\includegraphics[width=\linewidth]{heatmap_c}
	\caption*{(3) category C}\label{fig:heatmap_c}
	\endminipage
	\caption{Licensing between Stack Overflow code snippets and Qualitas Java file of 523 true online clone pairs}
\end{figure*}

@@

\section{Related Work}

Data on Stack Overflow can be exploited to support developers in several ways. Seahawk is an eclipse plug-in that can search and recommend relevant code snippets from Stack Overflow \cite{Ponzanelli2013}. Similarly, Prompter, ... \cite{Ponzanelli2014}.

\begin{itemize}
	\item Stack Overflow
	\begin{itemize}
		\item Code example \cite{Nasehi2012}
		\item Search for code in Stack Overflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014}
		\item Stack Overflow to help developers \cite{Ponzanelli2013, Ponzanelli2014}
		\item Improving Stack Oveflow \cite{Diamantopoulos2015, Wang2014, Bosu2013}
		\item Developers' behaviours on Stack Overlow \cite{Wang2013_StackOverflow, Movshovitz-Attias2013}
		\item Discuss \cite{Treude2016,Ahmed2015}
	\end{itemize}
	\item Code clones 
		\begin{itemize}
			\item Definition: Baxter et al. \cite{Baxter1998}
			\item Comparison of clone detectors: \cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}
			\item NiCad \cite{Roy2008,Cordy}
			\item Simian \cite{simian}
			\item Clone taxonomy \cite{Kapser2003}
			\item Clone evolution \cite{Pate2013,Mondal2011}
			\item Comparing Quality Metrics for Cloned and non cloned Java Methods: A Large Scale Empirical Study \cite{Saini2016}.
		\end{itemize}
	\item Agreement-based Clone Detection
	\begin{itemize}
		\item Bellon's framework \cite{Bellon2007}.
		\item EvaClone \cite{Wang2013}
		\item Hybrid \cite{Funaro2010}
	\end{itemize}
	\item Software licensing
	\item Outdated code \cite{Xia2014}
	\begin{itemize}
		\item Code siblings \cite{German2009}, Ninka -- Automatic indification of SW license \cite{German2010}, Evolution of SW licensing \cite{DiPenta2010}
	\end{itemize}
